---
title: "breeding consequences of the relative temperatures"
author: "david lopez idiaquez"
date: "2024-06-21"
output: html_document
---
Code to replicate the analyses in: "Optimal thermal niche-tracking buffers wild great tits against climate change" by David López-Idiáquez*, Ella F Cole, Charlotte E Regan & Ben C Sheldon

*contact:david.lopez-idiaquez[at]biology.ox.ac.uk

                 --------- Part 3: Linking temperature in the relative periods and reproductive success  --------- 

Load packages
```{r pacakges}
library(dplyr) #v. 1.1.3
library(lmerTest) #v. 3.1-3
library(lubridate) #v. 1.9.3
library(tidyr) #v. 1.3.0
library(glmmTMB) #v. 1.1.7
library(MCMCglmm) #v. 2.35
library(brms) #2.20.4
```

Load data
```{r}
join_data4 <- read.csv("join_data4.csv")
```

                                       #### -Hurdle models with the number of fledglings - ####
#prepare data for egg-laying                
```{r}
tem_lay<-join_data4 %>% #filter the data for these analyses
select(box, year, ld, Clutch_size, average_temperature_laying, Num_fledglings, Num_chicks, num_neighbors, Mother)

tem_lay$year<-as.factor(tem_lay$year)
tem_lay$ld<-as.numeric(tem_lay$ld)
tem_lay$Clutch_size<-as.numeric(tem_lay$Clutch_size)
tem_lay$Num_fledglings<-as.numeric(tem_lay$Num_fledglings)
tem_lay$Num_chicks<-as.numeric(tem_lay$Num_chicks)
tem_lay$num_neighbors<-as.numeric(tem_lay$num_neighbors)
tem_lay$Mother<-as.factor(tem_lay$Mother)
tem_lay<-as.data.frame(tem_lay)
```

#Model egg-laying number of fledgling
```{r}
#Temperature mean
bbdd_temp_laying_nf_temp<-tem_lay %>% 
  select(box, year, ld, Num_fledglings, Clutch_size, average_temperature_laying, Mother, num_neighbors) %>% 
  na.omit() 

bbdd_temp_laying_nf_temp<-as.data.frame(bbdd_temp_laying_nf_temp)

mod1_lay_nf_mtemp<-glmmTMB(Num_fledglings~
                             
                             scale(average_temperature_laying)+scale(I(average_temperature_laying^2))+
                             
                             scale(ld)+scale(num_neighbors)+
                       
                             (1|year)+(1|Mother), data=bbdd_temp_laying_nf_temp, 
                     
                             ziformula=~., family = "poisson")
summary(mod1_lay_nf_mtemp)
```

#prepare data for incubation (per1)
```{r}
tem_inc<-join_data4 %>% 
  select(box, year, ld, Clutch_size, average_temperature_per1, Num_fledglings, Num_chicks, num_neighbors, Mother)

tem_inc$year<-as.factor(tem_inc$year)
tem_inc$ld<-as.numeric(tem_inc$ld)
tem_inc$Clutch_size<-as.numeric(tem_inc$Clutch_size)
tem_inc$Num_fledglings<-as.numeric(tem_inc$Num_fledglings)
tem_inc$Num_chicks<-as.numeric(tem_inc$Num_chicks)
tem_inc$num_neighbors<-as.numeric(tem_inc$num_neighbors)
tem_inc$Mother<-as.factor(tem_inc$Mother)

tem_inc<-as.data.frame(tem_inc)
```

#Model incubation number of fledgling
```{r}
bbdd_temp_per1_nf_temp<-tem_inc %>% 
  select(box, year, ld, Num_fledglings, Clutch_size, average_temperature_per1, Mother, num_neighbors) %>% 
  na.omit() 

bbdd_temp_per1_nf_temp<-as.data.frame(bbdd_temp_per1_nf_temp)

mod1_per1_nf_mtemp<-glmmTMB(Num_fledglings~
                              scale(average_temperature_per1)+scale(I(average_temperature_per1^2))+
                             
                             scale(ld)+scale(num_neighbors)+
                       
                             (1|year)+(1|Mother), data=bbdd_temp_per1_nf_temp, 
                     
                             ziformula=~., family = "poisson")

summary(mod1_per1_nf_mtemp)
```

#prepare data for hatching (per2)
```{r}
tem_per2<-join_data4 %>% 
  select(box, year, ld, Clutch_size, average_temperature_per2, Num_fledglings, Num_chicks, num_neighbors, Mother)

tem_per2$year<-as.factor(tem_per2$year)
tem_per2$ld<-as.numeric(tem_per2$ld)
tem_per2$Clutch_size<-as.numeric(tem_per2$Clutch_size)
tem_per2$Num_fledglings<-as.numeric(tem_per2$Num_fledglings)
tem_per2$Num_chicks<-as.numeric(tem_per2$Num_chicks)
tem_per2$num_neighbors<-as.numeric(tem_per2$num_neighbors)
tem_per2$Mother<-as.factor(tem_per2$Mother)

tem_per2<-as.data.frame(tem_per2)
```

#Model hatching number of fledglings
```{r}
#Mean temperature
bbdd_m_temp_per2_nf<-tem_per2 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per2, num_neighbors, Mother) %>% 
  na.omit() 
  
bbdd_m_temp_per2_nf<-as.data.frame(bbdd_m_temp_per2_nf)

mod1_per2_nf_mtemp<-glmmTMB(Num_fledglings~
                             
                             scale(average_temperature_per2)+scale(I(average_temperature_per2^2))+
                             
                             scale(ld)+scale(num_neighbors)+
                       
                             (1|year)+(1|Mother), data=bbdd_m_temp_per2_nf, 
                     
                             ziformula=~., family = "poisson")

summary(mod1_per2_nf_mtemp)
```

#prepare data for nestling (per3)
```{r}
tem_per3<-join_data4 %>% 
  select(box, year, ld, Clutch_size, average_temperature_per3, Num_fledglings, Num_chicks, num_neighbors, Mother)

tem_per3$year<-as.factor(tem_per3$year)
tem_per3$ld<-as.numeric(tem_per3$ld)
tem_per3$Clutch_size<-as.numeric(tem_per3$Clutch_size)
tem_per3$Num_fledglings<-as.numeric(tem_per3$Num_fledglings)
tem_per3$Num_chicks<-as.numeric(tem_per3$Num_chicks)
tem_per3$num_neighbors<-as.numeric(tem_per3$num_neighbors)
tem_per3$Mother<-as.factor(tem_per3$Mother)

tem_per3<-as.data.frame(tem_per3)
``` 

#Model nestling number of fledglings
```{r}
#Mean temperature
bbdd_m_temp_per3_nf<-tem_per3 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per3, num_neighbors, Mother) %>% 
  na.omit() 
  
bbdd_m_temp_per3_nf<-as.data.frame(bbdd_m_temp_per3_nf)

mod1_per3_nf_mtemp<-glmmTMB(Num_fledglings~
                              scale(average_temperature_per3)+scale(I(average_temperature_per3^2))+
                             
                             scale(ld)+scale(num_neighbors)+
                       
                             (1|year)+(1|Mother), data=bbdd_m_temp_per3_nf, 
                     
                             ziformula=~., family = "poisson")

summary(mod1_per3_nf_mtemp)
```

#prepare data for fledgling (per4)
```{r}
tem_per4<-join_data4 %>% 
  select(box, year, ld, Clutch_size, average_temperature_per4, Num_fledglings, Num_chicks, num_neighbors, Mother)

tem_per4$year<-as.factor(tem_per4$year)
tem_per4$ld<-as.numeric(tem_per4$ld)
tem_per4$Clutch_size<-as.numeric(tem_per4$Clutch_size)
tem_per4$Num_fledglings<-as.numeric(tem_per4$Num_fledglings)
tem_per4$Num_chicks<-as.numeric(tem_per4$Num_chicks)
tem_per4$num_neighbors<-as.numeric(tem_per4$num_neighbors)
tem_per4$Mother<-as.factor(tem_per4$Mother)

tem_per4<-as.data.frame(tem_per4)
``` 

#Model fledgling number of fledgling 
```{r}
#Mean temperature
bbdd_m_temp_per4_nf<-tem_per4 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per4, num_neighbors, Mother) %>% 
  na.omit() 
  
bbdd_m_temp_per4_nf<-as.data.frame(bbdd_m_temp_per4_nf)

mod1_per4_nf_mtemp<-glmmTMB(Num_fledglings~ scale(average_temperature_per4)+scale(I(average_temperature_per4^2))+
                             
                             scale(ld)+scale(num_neighbors)+
                       
                             (1|year)+(1|Mother), data=bbdd_m_temp_per4_nf, 
                     
                             ziformula=~., family = "poisson")

summary(mod1_per4_nf_mtemp)
```

                                              #### -GLMM models with fledgling success - ####
#Model temp egg laying fledgling success
```{r}
bbdd_m_temp_laying_fs<-tem_lay %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_laying, num_neighbors, Mother) %>% 
  na.omit()

bbdd_m_temp_laying_fs$year<-as.factor(bbdd_m_temp_laying_fs$year)

mod1_m_temp_laying_fs<-glmer(cbind(Num_fledglings, (Clutch_size-Num_fledglings))~
                             scale(average_temperature_laying)+scale(I(average_temperature_laying^2))+
                             
                             scale(ld)+scale(Clutch_size)+scale(num_neighbors)+
                             
                             (1|year)+(1|Mother), 
                             
                             family="binomial", 
                             data=bbdd_m_temp_laying_fs)

summary(mod1_m_temp_laying_fs)
```

#Model temp incubation fledgling success
```{r}
bbdd_m_temp_per1_fs<-tem_inc %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per1, num_neighbors, Mother) %>% 
  na.omit()

bbdd_m_temp_per1_fs$year<-as.factor(bbdd_m_temp_per1_fs$year)

mod1_m_temp_per1_fs<-glmer(cbind(Num_fledglings, (Clutch_size-Num_fledglings))~
                             scale(average_temperature_per1)+scale(I(average_temperature_per1^2))+
                             
                             scale(ld)+scale(Clutch_size)+scale(num_neighbors)+
                             
                             (1|year)+(1|Mother), 
                             
                             family="binomial", 
                             data=bbdd_m_temp_per1_fs)

summary(mod1_m_temp_per1_fs)
```

#Model temp hatching fledgling success
```{r}
bbdd_m_temp_per2_fs<-tem_per2 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per2, num_neighbors, Mother) %>% 
  na.omit() 

bbdd_m_temp_per2_fs$year<-as.factor(bbdd_m_temp_per2_fs$year)

mod1_m_temp_per2_fs<-glmer(cbind(Num_fledglings, (Clutch_size-Num_fledglings))~
                             scale(average_temperature_per2)+scale(I(average_temperature_per2^2))+
                             
                             scale(ld)+scale(Clutch_size)+scale(num_neighbors)+
                             
                             (1|year)+(1|Mother), 
                             
                             family="binomial", 
                             data=bbdd_m_temp_per2_fs)

summary(mod1_m_temp_per2_fs)
```

#Model temp nestling fledgling success                                              
```{r}
bbdd_m_temp_per3_fs<-tem_per3 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per3, num_neighbors, Mother) %>% 
  na.omit()

bbdd_m_temp_per3_fs$year<-as.factor(bbdd_m_temp_per3_fs$year)

mod1_m_temp_per3_fs<-glmer(cbind(Num_fledglings, (Clutch_size-Num_fledglings))~
                             scale(average_temperature_per3)+scale(I(average_temperature_per3^2))+
                             
                             scale(ld)+scale(Clutch_size)+scale(num_neighbors)+
                             
                             (1|year)+(1|Mother), 
                             
                             family="binomial", 
                             data=bbdd_m_temp_per3_fs)

summary(mod1_m_temp_per3_fs)
```                                        

#Model temp fledgling fledgling success                                              
```{r temperature at laying effects on FS}
bbdd_m_temp_per4_fs<-tem_per4 %>% 
  select(box, year, ld, Clutch_size, Num_fledglings, average_temperature_per4, num_neighbors, Mother) %>% 
  na.omit()

bbdd_m_temp_per4_fs$year<-as.factor(bbdd_m_temp_per4_fs$year)

mod1_m_temp_per4_fs<-glmer(cbind(Num_fledglings, (Clutch_size-Num_fledglings))~
                             scale(average_temperature_per4)+scale(I(average_temperature_per4^2))+
                             
                             scale(ld)+scale(Clutch_size)+scale(num_neighbors)+
                             
                             (1|year)+(1|Mother), 
                             
                             family="binomial", 
                             data=bbdd_m_temp_per4_fs)

summary(mod1_m_temp_per4_fs)
```                                              
                                              
-Bayesian models: requiered to get the median optimal temperatures that maximise breeding success and their associated 95%CIs. For further information see SM-3.

Fledgling success
```{r}
bbdd_m_temp_laying_fs$Clutch_size<-as.integer(bbdd_m_temp_laying_fs$Clutch_size)
bbdd_m_temp_laying_fs$Num_fledglings<-as.integer(bbdd_m_temp_laying_fs$Num_fledglings)
                                              
#laying
mod_lay_fs<-brm(Num_fledglings | trials(Clutch_size) ~ (average_temperature_laying)+(I(average_temperature_laying^2))+
           (ld)+(Clutch_size)+(num_neighbors)+(1|year)+(1|Mother),
  family = binomial("logit"),
  data = bbdd_m_temp_laying_fs,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_lay_fs, digits=3)  
#saving the model output is recommended as they take some time to run.

#per1
mod_per1_fs<-brm(Num_fledglings | trials(Clutch_size) ~ (average_temperature_per1)+(I(average_temperature_per1^2))+
           (ld)+(Clutch_size)+(num_neighbors)+(1|year)+(1|Mother),
  family = binomial("logit"),
  data = bbdd_m_temp_per1_fs,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per1_fs, digits=3)  

#per2
mod_per2_fs<-brm(Num_fledglings | trials(Clutch_size) ~ (average_temperature_per2)+(I(average_temperature_per2^2))+
           (ld)+(Clutch_size)+(num_neighbors)+(1|year)+(1|Mother),
  family = binomial("logit"),
  data = bbdd_m_temp_per2_fs,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per2_fs, digits=3)  

#per3
mod_per3_fs<-brm(Num_fledglings | trials(Clutch_size) ~ (average_temperature_per3)+(I(average_temperature_per3^2))+
           (ld)+(Clutch_size)+(num_neighbors)+(1|year)+(1|Mother),
  family = binomial("logit"),
  data = bbdd_m_temp_per3_fs,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per3_fs, digits=3)

#per4
mod_per4_fs<-brm(Num_fledglings | trials(Clutch_size) ~ (average_temperature_per4)+(I(average_temperature_per4^2))+
           (ld)+(Clutch_size)+(num_neighbors)+(1|year)+(1|Mother),
  family = binomial("logit"),
  data = bbdd_m_temp_per4_fs,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per4_fs, digits=3)

```

#Number of fledglings - Probability of brood failure
```{r}
#egg-laying
bbdd_temp_laying_nf_temp <- bbdd_temp_laying_nf_temp %>%
  mutate(Num_fledglings_code = case_when(
    Num_fledglings == 0 ~ 1,    
    Num_fledglings > 0 ~ 0,     
    TRUE ~ Num_fledglings       
  ))

bbdd_temp_laying_nf_temp<-as.data.frame(bbdd_temp_laying_nf_temp)
bbdd_temp_laying_nf_temp$Num_fledglings_code<-as.factor(bbdd_temp_laying_nf_temp$Num_fledglings_code)

mod_lay_nf_code<-brm(Num_fledglings_code ~ (average_temperature_laying)+(I(average_temperature_laying^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = bernoulli,
  data = bbdd_temp_laying_nf_temp,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_lay_nf_code, digits=3)

#Incubation
bbdd_temp_per1_nf_temp <- bbdd_temp_per1_nf_temp %>%
  mutate(Num_fledglings_code = case_when(
    Num_fledglings == 0 ~ 1,    
    Num_fledglings > 0 ~ 0,     
    TRUE ~ Num_fledglings       
  ))

bbdd_temp_per1_nf_temp<-as.data.frame(bbdd_temp_per1_nf_temp)

mod_per1_nf_code<-brm(Num_fledglings_code ~ (average_temperature_per1)+(I(average_temperature_per1^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = bernoulli,
  data = bbdd_temp_per1_nf_temp,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per1_nf_code, digits=3) 

#Hatching
bbdd_m_temp_per2_nf <- bbdd_m_temp_per2_nf %>%
  mutate(Num_fledglings_code = case_when(
    Num_fledglings == 0 ~ 1,    
    Num_fledglings > 0 ~ 0,     
    TRUE ~ Num_fledglings       
  ))

bbdd_m_temp_per2_nf<-as.data.frame(bbdd_m_temp_per2_nf)

mod_per2_nf_code<-brm(Num_fledglings_code ~ (average_temperature_per2)+(I(average_temperature_per2^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = bernoulli,
  data = bbdd_m_temp_per2_nf,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per2_nf_code, digits=3) 

#Nestling
bbdd_m_temp_per3_nf <- bbdd_m_temp_per3_nf %>%
  mutate(Num_fledglings_code = case_when(
    Num_fledglings == 0 ~ 1,    
    Num_fledglings > 0 ~ 0,     
    TRUE ~ Num_fledglings       
  ))

bbdd_m_temp_per3_nf<-as.data.frame(bbdd_m_temp_per3_nf)

mod_per3_nf_code<-brm(Num_fledglings_code ~ (average_temperature_per3)+(I(average_temperature_per3^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = bernoulli,
  data = bbdd_m_temp_per3_nf,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per3_nf_code, digits=3)

#Fledging
bbdd_m_temp_per4_nf <- bbdd_m_temp_per4_nf %>%
  mutate(Num_fledglings_code = case_when(
    Num_fledglings == 0 ~ 1,    
    Num_fledglings > 0 ~ 0,     
    TRUE ~ Num_fledglings       
  ))

bbdd_m_temp_per4_nf<-as.data.frame(bbdd_m_temp_per4_nf)

mod_per4_nf_code<-brm(Num_fledglings_code ~ (average_temperature_per4)+(I(average_temperature_per4^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = bernoulli,
  data = bbdd_m_temp_per4_nf,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per4_nf_code, digits=3)
```

#Number of fledlings - Non-zero part of the data
```{r}
#egg-laying
bbdd_temp_laying_nf_temp_nfzero <- bbdd_temp_laying_nf_temp %>%
  filter(Num_fledglings>0)
  
bbdd_temp_laying_nf_temp_nfzero<-as.data.frame(bbdd_temp_laying_nf_temp_nfzero)

mod_lay_nf_code_zero<-brm(Num_fledglings ~ (average_temperature_laying)+(I(average_temperature_laying^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = poisson,
  data = bbdd_temp_laying_nf_temp_nfzero,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_lay_nf_code_zero, digits=3)

#incubation
bbdd_temp_per1_nf_temp_nfzero <- bbdd_temp_per1_nf_temp %>%
  filter(Num_fledglings>0)
  
bbdd_temp_per1_nf_temp_nfzero<-as.data.frame(bbdd_temp_per1_nf_temp_nfzero)

mod_per1_nf_code_zero<-brm(Num_fledglings ~ (average_temperature_per1)+(I(average_temperature_per1^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = poisson,
  data = bbdd_temp_per1_nf_temp_nfzero,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per1_nf_code_zero, digits=3)

#Hatching
bbdd_m_temp_per2_nf_nfzero <- bbdd_m_temp_per2_nf %>%
  filter(Num_fledglings>0)
  
bbdd_m_temp_per2_nf_nfzero<-as.data.frame(bbdd_m_temp_per2_nf_nfzero)

mod_per2_nf_code_zero<-brm(Num_fledglings ~ (average_temperature_per2)+(I(average_temperature_per2^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = poisson,
  data = bbdd_m_temp_per2_nf_nfzero,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per2_nf_code_zero, digits=3)

#Nestling
bbdd_m_temp_per3_nf_nfzero <- bbdd_m_temp_per3_nf %>%
  filter(Num_fledglings>0)
  
bbdd_m_temp_per3_nf_nfzero<-as.data.frame(bbdd_m_temp_per3_nf_nfzero)

mod_per3_nf_code_zero<-brm(Num_fledglings ~ (average_temperature_per3)+(I(average_temperature_per3^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = poisson,
  data = bbdd_m_temp_per3_nf_nfzero,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per3_nf_code_zero, digits=3)

#Fledgling
bbdd_m_temp_per4_nf_nfzero <- bbdd_m_temp_per4_nf %>%
  filter(Num_fledglings>0)
  
bbdd_m_temp_per4_nf_nfzero<-as.data.frame(bbdd_m_temp_per4_nf_nfzero)

mod_per4_nf_code_zero3<-brm(Num_fledglings ~ (average_temperature_per4)+(I(average_temperature_per4^2))+
           (ld)+(num_neighbors)+(1|year)+(1|Mother),
  family = poisson,
  data = bbdd_m_temp_per4_nf_nfzero,
  chains = 4,
  cores = 4,
  iter = 10000,
  warmup = 2000,
  thin = 10)

print(mod_per4_nf_code_zero3, digits=3)

```


How to get the data from the Bayesian models to calculate the median ± 95 CIs. I only show one example but the process is the same for all models.

Even if the models do not take that long to run, I would recommend to save them once their finish

```{r}
#load your model

#get the posterior estimates for the quadratic component of temperature 
post_mod_lay_fs_1_q <- as.data.frame(as_draws(mod_lay_fs)[[1]]$b_Iaverage_temperature_layingE2)
colnames(post_mod_lay_fs_18.061_q) <- "meant2"
post_mod_lay_fs_2_q <- as.data.frame(as_draws(mod_lay_fs)[[2]]$b_Iaverage_temperature_layingE2)
colnames(post_mod_lay_fs_18.062_q) <- "meant2"
post_mod_lay_fs_3_q <- as.data.frame(as_draws(mod_lay_fs)[[3]]$b_Iaverage_temperature_layingE2)
colnames(post_mod_lay_fs_18.063_q) <- "meant2"
post_mod_lay_fs_4_q <- as.data.frame(as_draws(mod_lay_fs)[[4]]$b_Iaverage_temperature_layingE2)
colnames(post_mod_lay_fs_18.064_q) <- "meant2"

#join them in a sigle dataset 
est_q_fs<-rbind(post_mod_lay_fs1_q, post_mod_lay_fs2_q)
est_q_fs<-rbind(est_q_fs, post_mod_lay_fs3_q)
est_q_fs<-rbind(est_q_fs, post_mod_lay_fs4_q)

#get the posterior estimates for the linear component of temperature 
post_mod_lay_fs_1_l <- as.data.frame(as_draws(mod_lay_fs)[[1]]$b_average_temperature_laying)
colnames(post_mod_lay_fs_1_l) <- "meant_lin"
post_mod_lay_fs_2_l <- as.data.frame(as_draws(mod_lay_fs)[[2]]$b_average_temperature_laying)
colnames(post_mod_lay_fs_2_l) <- "meant_lin"
post_mod_lay_fs_3_l <- as.data.frame(as_draws(mod_lay_fs)[[3]]$b_average_temperature_laying)
colnames(post_mod_lay_fs_3_l) <- "meant_lin"
post_mod_lay_fs_4_l <- as.data.frame(as_draws(mod_lay_fs)[[4]]$b_average_temperature_laying)
colnames(post_mod_lay_fs_4_l) <- "meant_lin"

est_l_fs<-rbind(post_mod_lay_fs_1_l, post_mod_lay_fs_2_l)
est_l_fs<-rbind(est_l_fs, post_mod_lay_fs_3_l)
est_l_fs<-rbind(est_l_fs, post_mod_lay_fs_4_l)

#join the two datasets with the estimates
join_lay_fs<-cbind(est_q_fs, est_l_fs)

#here i compute the the vertex of the parabola to get the temperature at which the reproduction (in this case fledgling success) is higher throguh all values in the posterior distribution.
join_lay_fs<-join_lay_fs %>% 
  mutate(lay_temp_maxnf=((-meant_lin)/(2*meant2)))

#get the mean, median and 95%CI 
mean(join_lay_fs$lay_temp_maxnf) 
median(join_lay_fs$lay_temp_maxnf) 
HPDinterval(as.mcmc(join_lay_fs$lay_temp_maxnf)) 
```




