---
title: "thermal tracking and mismatch caterpillars"
author: "david lopez idiaquez"
date: "2024-06-24"
output: html_document
---
Code to replicate the analyses in: "Optimal thermal niche-tracking buffers wild great tits against climate change" by David López-Idiáquez*, Ella F Cole, Charlotte E Regan & Ben C Sheldon

*contact:david.lopez-idiaquez[at]biology.ox.ac.uk

          --------- Part 4: Thermal tracking caterpillars & mismatch  --------- 

Load packages
```{r pacakges}
library(dplyr) #v. 1.1.3
library(lmerTest) #v. 3.1-3
library(lubridate) #v. 1.9.3
library(tidyr) #v. 1.3.0
```

0. Load caterpillar half-fall data
```{r}
HF_data <- read.csv("Half_fall_data.csv")
```

1. Temporal trends in the caterpillar half-fall
```{r}
mod1<-lm(Half_fall_date~Year, data=HF_data)
summary(mod1)
anova(mod1)
```

2.Load climate data
```{r}
max_min<-read.csv("clim_data.csv")
#compute mean temperature and create julday
mean_temp<-max_min %>% 
  mutate(tmean=(max+min)/2) %>%
  group_by(year) %>% 
  mutate(julday=row_number())
```

2.1 Thermal niche tracking caterpillars - compute mean temperatures with different interval lenghts
```{r}
#convert caterpillar date to 1 of January 
HF_data2<-HF_data %>% 
  mutate(Hf_2=Half_fall_date+90) %>% 
  na.omit() %>% 
  filter(Year>1964) %>% 
  mutate(Hf2_r=round(Hf_2, digits = 0)) 

## Function to calculate mean temperature and standard error for days over and under a date by year
#7days (this function can be used to compute the mean temperatures for the other time intervals)
calculate_mean_and_se <- function(year, julday) {
  subset_temp <- mean_temp[mean_temp$year == year & mean_temp$julday >= (julday - 7) & mean_temp$julday <= (julday + 7), ]
  mean_temperature <- mean(subset_temp$tmean, na.rm = TRUE)
  se_temperature <- sd(subset_temp$tmean, na.rm = TRUE) / sqrt(nrow(subset_temp))
  n_temperature <- nrow(subset_temp)
  return(c(mean_temperature, se_temperature, n_temperature))
}

# Apply the function to each row in HF_data2
result <- t(mapply(calculate_mean_and_se, HF_data2$Year, HF_data2$Hf2_r))
colnames(result) <- c("mean_temperature", "se_temperature", "n_temperature")

# Combine results with HF_data2
HF_data2 <- cbind(HF_data2, result)

#Test that the function is doing what is expected to do
# 1965 - 148.4 - 11.62 (temperature obtained from the function)
mean_temp_1965<-mean_temp %>% 
  filter(year==1965) %>% 
  filter(julday>=(148-7) & julday<=(148+7)) %>% 
  mutate(meantemp=mean(tmean)) #mean temp manually 11.62

#model temporal trends in mean temperature
mod2<-lm(mean_temperature~Year, data=HF_data2)
summary(mod2)
anova(mod2)
```

Links between temperature in the relative periods and mismatch with the caterpillar peak
```{r}
#Load match data
match<-read.csv("match.csv")
```

Models
```{r}
#egg-laying
mod1<-lmer(abs(mismatch)~average_temperature_laying+I(average_temperature_laying^2)+(1|year)+(1|Mother), data=match)
summary(mod1)
anova(mod1, type=3)

#Incubation
mod2<-lmer(abs(mismatch)~average_temperature_per1+I(average_temperature_per1^2)+(1|year)+(1|Mother), data=match)
summary(mod2)
anova(mod2, type=3)

#Hatching
mod3<-lmer(abs(mismatch)~average_temperature_per2+I(average_temperature_per2^2)+(1|year)+(1|Mother), data=match)
summary(mod3)
anova(mod3, type=3)

#Nestling
mod4<-lmer(abs(mismatch)~average_temperature_per3+I(average_temperature_per3^2)+(1|year)+(1|Mother), data=match)
summary(mod4)
anova(mod4, type=3)
```



