---
title: "Temporal trends in temperature using fixed intervals"
author: "david lopez idiaquez"
date: 01-07-2024
output: html_document
---

Code to replicate the analyses in: "Optimal thermal niche-tracking buffers wild great tits against climate change" by David López-Idiáquez*, Ella F Cole, Charlotte E Regan & Ben C Sheldon

*contact:david.lopez-idiaquez[at]biology.ox.ac.uk

        ---------------------   Temporal trends in temperature using a fixed time interval ---------------------   
Load packages (R version 4.3.1)
```{r load packages, include=FALSE, message = FALSE}
library(dplyr) #v. 1.1.3
library(lmerTest) #v. 3.1-3
library(lubridate) #v. 1.9.3
library(tidyr) #v. 1.3.0
library(confintr) #v. 1.0.2
```

 ---------------------   Temporal trends in the fixed interval (from February 15 to June 5) ---------------------   
-Load the climate data [Obtained from: Central England dataset at the Met Office Hadley Centre (https://www.metoffice.gov.uk/hadobs/)]
```{r}
##Climate data
max_min<-read.csv("clim_data.csv")
#compute mean temperature and julday
mean_temp<-max_min %>% 
  mutate(tmean=(max+min)/2) %>% 
  group_by(year) %>% 
  mutate(julday=row_number()) %>% 
  ungroup()
```
-Select relevant columns and prepare the interval of interest
```{r}
mean_temp2<-mean_temp %>% 
  select(year, tmean, max, julday)
#period of interest to compute the yearly average temperatures
periods<- list(
  fullper = c(46, 156)) #46 represents the 15th of Feb. 156 represents the 5th of June
```
-Loop to compute year mean and se temperature.
```{r}
#list to store the results
avg_temp_results <- list() 

#Loop to collate the mean temperature and se the interval each year.
for (period_name in names(periods)) {
  start_day <- periods[[period_name]][1]
  end_day <- periods[[period_name]][2]
  
 
  avg_temp <- mean_temp2 %>%
    filter(julday >= start_day & julday <= end_day) %>%
    group_by(year) %>%
    summarize(avg_temp = mean(tmean), #mean
              se_temp = (sd(tmean)/sqrt(length(tmean)))) #se
  
  avg_temp_results[[period_name]] <- avg_temp
}

#transform into a dataset
avg_temp_data_frames <- lapply(avg_temp_results, as.data.frame)

combined_data_tmean <- bind_rows(avg_temp_data_frames, .id = "period_name")

yearly_temp_meansse <- combined_data_tmean %>%
  pivot_wider(names_from = period_name, values_from = c(avg_temp, se_temp))

names <- c("year", "fix_inter_tmean", "fix_inter_tmean_se") #rename columns
colnames(yearly_temp_meansse)<-names
```
-Run the linear model
```{r}
#Explore the temporal trends in mean temperature
mod_tmean1<-lm(fix_inter_tmean~year, data=yearly_temp_meansse)
summary(mod_tmean1) 
anova(mod_tmean1)
confint(mod_tmean1, "year")
```

---------------------   Temporal trends in biologically relevant intervals  ---------------------
  #Function to compute the temporal trends in all intervals within two dates
```{r}
fit_linear_models_all_intervals_fixed <- function(data, min_window_size, max_window_size, start_day, end_day) {
  results <- data.frame()  
  
  for (window_size in min_window_size:max_window_size) {
    for (i in start_day:(end_day - window_size + 1)) {
      window_data <- data %>%
        filter(julday >= i & julday <= i + window_size - 1)
      
      if (nrow(window_data) >= window_size) {
        
        window_data <- window_data %>%
          group_by(year) %>%
          summarize(Mean_Temperature = mean(tmean, na.rm = TRUE)) 
        
        model <- lm(Mean_Temperature ~ year, data = window_data)
        
        coef <- coef(model)
        std_error <- summary(model)$coefficients[, "Std. Error"]
        p_value <- summary(model)$coefficients[, "Pr(>|t|)"]
        
        results <- rbind(results, data.frame(
          Window_Start = i,
          Window_End = i + window_size - 1,
          Window_Size = window_size,
          Intercept_Coefficient = coef[1],
          Year_Coefficient = coef[2],
          Year_Std_Error = std_error[2],
          Year_P_Value = p_value[2]
        ))
      }
    }
  }
  
  return(results)
}
```
  #Filter the climate dataset to retain the relevant interval, not needed in these analyses
```{r}
interval0<-mean_temp2 %>% 
  select(year, julday, tmean, max) %>% 
  filter(julday>=46 & julday<=156) #el periodo largo desde el dia que yo identifico, hasta el fin de la reproduccion.

interval<-subset(interval0, year>1964) #quito este año que no entra en mi estudio
```
  #Use the function to get the data
```{r aplicar funcion}
#Here, I define the window size and the start and end days where to fit this windows. 
min_window_size <- 8
max_window_size <- 15
start_day <- 46
end_day <- 156

results_interval <- fit_linear_models_all_intervals_fixed(interval, min_window_size, max_window_size, start_day, end_day)

mean(results_interval$Year_Coefficient) #mean trend [0.03042948*59=1.79]

#Coefficients
Year_Coefficient <- results_interval$Year_Coefficient
#Sd
sd_val <- sd(Year_Coefficient)
#N
n <- length(Year_Coefficient)
#se
se <- sd_val / sqrt(n)
#tvalue
t_value <- qt(0.975, df = n-1)
#95% CI
CI_lower <- mean(results_interval$Year_Coefficient) - t_value * se #[0.02978222*59=1.757151]
CI_upper <- mean(results_interval$Year_Coefficient) + t_value * se #[0.03107675*59=1.833528]
#ci
list(lower = CI_lower, upper = CI_upper)
```

---------------------   Explore that the function does what is supposed to do ---------------------   
a. manually compute trends
```{r}
#This is to compare the mean temperatures that I get from the function to those computed manually
#test1: ten day window between day 62 and day 71
test1<-interval %>%
  filter(julday >= 62 & julday <= 71) %>%
  group_by(year) %>% 
  summarise(meantmean=mean(tmean)) 
#model 1
mod_test1<-lm(meantmean ~ year, data = test1)
summary(mod_test1) #results form the loop: 0.02428638 ± 0.01477908, p=0.1058275
                   #results from test: 0.02429 ± 0.01478, p=0.106

#test2: 14 day window between day 83 and day 96
test2<-interval %>%
  filter(julday >= 83 & julday <= 96) %>%
  group_by(year) %>% 
  summarise(meantmean=mean(tmean)) 
#model 2
mod_test2<-lm(meantmean ~ year, data = test2)
summary(mod_test2) #results form the loop: 0.03765801 ± 0.01227705, p=0.003301003
                   #results from test: 0.03766 ± 0.01228, p=0.00330
#The function works gives 
```
b. calculate the number of intervals that fit in my window of interest.
```{r}
#range of days
start_day_prueba <- 46
end_day_prueba <- 156

#interval size
periods <- c(8, 9, 10, 11, 12, 13, 14, 15)

#count
total_periods <- 0

# Iterate through each possible starting day
for (start in start_day_prueba:(end_day_prueba - 1)) {
  # Check if a valid period can be formed for each length
  for (period in periods) {
    if (start + period - 1 <= end_day_prueba) {
      total_periods <- total_periods + 1
    }
  }
}
total_periods

#total periods: 804 which are the same obtained with the function.
```

                  





